---
title: "Getting Started with tidylens"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with tidylens}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", eval = FALSE)
```

Tidylens is a classical, local-first toolkit for film-frame analysis in R. It converts video files into tidy `tl_frames` tibbles, adds inspectable visual features, and detects shots and shot scales.

The v3.x API is intentionally narrow: no CNNs, no cloud APIs, and no opaque model services.

## Install

```{r}
devtools::install_github("nabsiddiqui/tidylens")
install.packages("av")
```

## Extract Frames

```{r}
library(tidylens)

frames <- video_extract_frames_by_seconds("movie.mp4", every = 5)
frames
```

Other frame getters:

```{r}
even_frames <- video_extract_frames_evenly("movie.mp4", n = 100)
keyframes <- video_extract_keyframes("movie.mp4")
```

`keyframes` are codec I-frames. They are useful for fast visual sampling, but they are not shot boundaries and do not carry shot durations.

## Extract Shots

```{r}
shots <- video_extract_shots("movie.mp4")
```

Shot rows include `start_time`, `end_time`, and `duration`. To classify shot scale, pipe the result into `frame_classify_scale()`:

```{r}
shots <- shots |> frame_classify_scale()
```

## Add Visual Features

```r
shots <- shots |>
  frame_extract_brightness() |>
  frame_extract_colourfulness() |>
  frame_extract_warmth() |>
  frame_extract_fluency_metrics() |>
  frame_extract_glcm() |>
  frame_extract_color_histogram()
```

Common feature families:

| Family | Examples |
|--------|----------|
| Color | `frame_extract_brightness()`, `frame_extract_colourfulness()`, `frame_extract_warmth()` |
| Composition | `frame_extract_fluency_metrics()`, `frame_extract_rule_of_thirds()`, `frame_extract_center_bias()` |
| Texture | `frame_extract_glcm()`, `frame_extract_sharpness()`, `frame_extract_contrast()` |
| Detection | `frame_detect_faces()` |
| Classification | `frame_classify_scale()` |
| Vector representations | `frame_extract_color_histogram()`, `frame_extract_lbp_histogram()` |

## Complete Pipeline

```{r}
shots <- video_extract_shots("movie.mp4") |>
  frame_classify_scale() |>
  frame_extract_colourfulness() |>
  frame_extract_warmth() |>
  frame_extract_fluency_metrics()
```

## Function Families

| Family | Functions |
|--------|-----------|
| Video | `video_download()`, `video_get_info()` |
| Video extraction | `video_extract_frames_by_seconds()`, `video_extract_frames_evenly()`, `video_extract_keyframes()`, `video_extract_shots()` |
| Frame features | `frame_extract_*()`, `frame_detect_faces()`, `frame_classify_scale()` |
| Utilities | `is_tl_frames()` |
